---
title: "p8105_hw5_jt3098"
author: "Jieqi Tu (jt3098)"
date: "11/4/2018"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(rvest)
```

## Problem 1
```{r file names defining}
# Create a data frame that contains all file names
longitudinal_data = 
  tibble(list.files(path = "./data"))

# Rename the column name of the first variable
colnames(longitudinal_data)[1] = 'file'
```

```{r read in files}
# Create a function to read in files
read_data = function(file) {
  data = 
    read.csv(str_c("./data/", file)) %>%
    as.data.frame()
  
 data
}

# Load files in using created function above
longitudinal_data =
  longitudinal_data %>%
  mutate(data = map(longitudinal_data$file, read_data)) # All data from one file are nested in one variable called "data"
```

```{r data tidying}
# Spread out the data set
longitudinal_data = 
  longitudinal_data %>%
  unnest() %>% # unnest the `data` variable to obtain more variables to store the data
  gather(key = week, value = value, week_1:week_8) # make week be a single variable

# Separate the control and experiment groups
longitudinal_data = 
  longitudinal_data %>%
  separate(file, into = c("group_type", "number"), sep = "_") %>%
  separate(number, into = c("ID", "extension"), sep = 2) %>%
  select(-extension)

# Manipulate the "week" variable
longitudinal_data = 
  longitudinal_data %>%
  separate(week, into = c("character", "week_number"), sep = 5) %>%
  select(-character)

# Revise the name of arms
longitudinal_data$group_type = str_replace(longitudinal_data$group_type, "con", "control")
longitudinal_data$group_type = str_replace(longitudinal_data$group_type, "exp", "experimental")

# Change the column type of "week_number"
longitudinal_data$week_number = as.numeric(longitudinal_data$week_number)
```

```{r speghetti plot for problem 1}
# Make a new variable for each subject to have a more clear order
longitudinal_data$subject = str_c(longitudinal_data$group_type, '_', longitudinal_data$ID)

# Make a speghetti plot to show the trend of observation data from each arm
longitudinal_data %>%
  ggplot(aes(x = week_number, y = value, group = subject, color = group_type)) +
  geom_line(alpha = 0.5) + 
  geom_point(alpha = 0.2) +
  labs(
    title = "Observations on Each Subject Over Time",
    x = "Week",
    y = "Observation Data"
  ) +
  theme_bw()
```

Comments:
From this plot, we could know that, in general, experimental groups have higher observational values than control groups. Additionally, the overall trend for experimental groups is increasing over time, while there is relatively no big difference in control groups.

## Problem 2
```{r importing data, message = FALSE}
# Importing data for problem 2
homicide_data = read_csv("./data2/homicide-data.csv")
```

```{r calculating NAs}
# Calculate the the number of NAs in each column 
n_NA = 
  sapply(homicide_data, function(x) sum(length(which(is.na(x))))) %>%
  knitr::kable()
n_NA
```

Descriptions about the raw data:

* There are `r nrow(homicide_data)` rows and `r ncol(homicide_data)` columns in this dataset.
* There are 2999 NA values in "victim_age" variable, and 60 NAs in "lat" and "lon" respectively.
* This dataset has 52179 observations.
* The variables inlude ID, reported date, the last and first name of victims, the sex, race and age of victims, the city and state, longitude and latitude, and the deposition status.

```{r city_state summarizing}
# Make a new variable to summarize the city and state informtion
homicide_data = 
  homicide_data %>%
  mutate(city_state = str_c(city, ", ", state)) %>%
  select(-city, -state)
```

```{r calculate the total number of cases and unsolved cases by city}
# Calculate the total number of cases of homicide
homicide_data_summary = 
  homicide_data %>%
  group_by(city_state) %>%
  mutate(n_homicide = n())

# Calculate the total number of unsolved cases
homicide_data_summary = 
  homicide_data_summary %>%
  filter(disposition %in% c("Open/No arrest", "Closed without arrest")) %>%
  group_by(city_state) %>%
  mutate(n_unsolved = n())

# Summarize the total number of cases and unsolved cases by city and state
homicide_data_summary = 
  homicide_data_summary %>%
  distinct(city_state, n_homicide, n_unsolved) %>%
  knitr::kable()

# Check the number of cases and unsolved
homicide_data_summary
```

```{r prop.test}

```

